---
title: "Laundro-Hydro Startup"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(ggplot2)
library(sp)

NYCCensus <- read_sf("/Users/kamal/Documents/GitHub/Laundro-Hydro Startup/Shapefiles/2010 Census Tracts/geo_export_430aa5ff-9cc1-4b07-b3a2-f0ad4cbbda6e.shp")
NTAs <- read_sf("/Users/kamal/Documents/GitHub/Laundro-Hydro Startup/Shapefiles/Neighborhood Tabulation Areas/geo_export_312d1a91-c0f7-4fc0-a998-626c0f4e2c69.shp")
Laundromats <- read.csv("/Users/kamal/Documents/GitHub/Laundro-Hydro Startup/GeocodeResults.csv")
USCensus <- read.csv("/Users/kamal/Documents/GitHub/Laundro-Hydro Startup/ACS_17_5YR_S0101/ACS_17_5YR_S0101_with_ann.csv")
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
```{r}
USCensus <- USCensus[-1,]
USCensus$CensusID <- substring(as.character(USCensus$GEO.id2),5)
#newdata <- View(USCensus[order(-USCensus$GEO.id2),])
#Get rid of NAs for now
Laundromats <- na.omit(Laundromats)

#Get rid of scientific notations
options("scipen"=100, "digits"=4)


#Converts coordinates of Laundromats to spatial coordinates
Laundromats <- SpatialPointsDataFrame(coords = Laundromats[,c(6,7)], data = Laundromats,
 proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))
options(digits = 5)

#Converts it to sf
Laundromats <- sf::st_as_sf(Laundromats, coords = c("Longitude","Latitude"))

RidChar <- function(x) return(sapply (strsplit(x , '[*]' ), `[` , 1))

View(RidChar(as.character(Laundromats$Average.Rating.on.Yelp)))

ggplot() + 
 geom_sf(data = NTAs) +
 geom_point(data = Laundromats, aes(Longitude, Latitude, color = Latitude))
```

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
